Reproducibility in plant pathology: where do we stand and a way forward

### 2021-09-01 analysis/paper/paper.Rmd
github/Github -> GitHub

At the second level, Lehner _et al._ [-@Lehner2017] used GitHub to host a code repository of their research compendium website with data and a reproducible report that explains in detail all steps of the analysis and the R code for conducting a meta-analysis for assessing heterogeneity in the relationship between white mold incidence and soybean yield and between incidence and soybean yield ([https://emdelponte.github.io/paper-white-mold-meta-analysis/](https://emdelponte.github.io/paper-white-mold-meta-analysis/)).
The website clearly demonstrates the analysis to readers and uses R so that anyone can easily replicate the work.
Likewise, Duku _et al._ [-@Duku2016] provide scripts for models, data and code for graphs, via a website hosted by GitHub, [http://adamhsparks.github.io/MICCORDEA/](http://adamhsparks.github.io/MICCORDEA/), that can be used to replicate their study modelling the effects of climate change on rice bacterial blight and rice leaf blast in Tanzania. 
A final example is provided by Carleson et al. [-@carleson2019population] who hosted the code for reproducing a population genomic analysis of  _Phytophthora plurivora_ on github, while providing all data on OSF.

The third level is the use of proper data repositories such as Github, FigShare, Zenodo or OSF.io among others, allow for the deposition and updating of code, figures, data preprints or any other materials that support the article itself while providing a DOI and citation for a standalone citation.
Sparks _et al._ [-@Sparks2011; -@Sparks2014] used FigShare to provide models, data and code, [@Sparks2016] necessary to replicate model development and the subsequent study on the effects of climate change on potato late blight.
Similarly, Carleson et al. [-@carleson2019population] provided all data on OSF [-@Carleson_Grünwald_2019].

>>>>

At the second level, Lehner _et al._ [-@Lehner2017] used GitHub to host a code repository of their research compendium website with data and a reproducible report that explains in detail all steps of the analysis and the R code for conducting a meta-analysis for assessing heterogeneity in the relationship between white mold incidence and soybean yield and between incidence and soybean yield ([https://emdelponte.github.io/paper-white-mold-meta-analysis/](https://emdelponte.github.io/paper-white-mold-meta-analysis/)).
The website clearly demonstrates the analysis to readers and uses R so that anyone can easily replicate the work.
Likewise, Duku _et al._ [-@Duku2016] provide scripts for models, data and code for graphs, via a website hosted by GitHub, [http://adamhsparks.github.io/MICCORDEA/](http://adamhsparks.github.io/MICCORDEA/), that can be used to replicate their study modelling the effects of climate change on rice bacterial blight and rice leaf blast in Tanzania. 
A final example is provided by Carleson et al. [-@carleson2019population] who hosted the code for reproducing a population genomic analysis of  _Phytophthora plurivora_ on GitHub, while providing all data on OSF.

The third level is the use of proper data repositories such as GitHub, FigShare, Zenodo or OSF.io among others, allow for the deposition and updating of code, figures, data preprints or any other materials that support the article itself while providing a DOI and citation for a standalone citation.
Sparks _et al._ [-@Sparks2011; -@Sparks2014] used FigShare to provide models, data and code, [@Sparks2016] necessary to replicate model development and the subsequent study on the effects of climate change on potato late blight.
Similarly, Carleson et al. [-@carleson2019population] provided all data on OSF [-@Carleson_Grünwald_2019].
